---
name: Amul Kumar
surname: Acharya
position: "Research/Remote Sensing Officer"
address: "Kathmandu,Nepal"
profilepic: "./img/me2.png"
email: "acharya.amulkumar@gmail.com"
github: acharyaamul
linkedin: Amulkumar Acharya
twitter: pricelessamul
orcid: 0000-0002-3638-6692
phone: +977 9851184438
date: "`r format(Sys.time(), '%B %Y')`"
fontawesome: yes
headcolor: 990000
aboutme: "I have been working as Research/Remote Sensing Officer for ten years at Forest Reserch and Training Centre, Nepal. I have a deep driven passion for application of Remote sensing and GIS techniques in Forestry sector."
docname: CV
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)

require(xfun)

packages <- c('vitae'     # The CV's LaTeX Template
             ,'tibble'    # Data structure for tribbles
             ,'magrittr'  # The Pipe %>%
             ,'here'      # Relative File Paths
             ,'readr'     # Data Loading
             ,'glue'      # String Manipulation
            )

xfun::pkg_attach2(packages, message = FALSE)

source(file = here("r","data.r"))

```

# Employment

```{r EMPLOYMENT}

work %>%
  detailed_entries(
    with = title,
    what = unit,
    why = detail,
    when = glue::glue("{startMonth} {startYear} --> {endMonth} {endYear}",.na = ""),
    where = where
  )

```

# Education

```{r EDUCATION}

edu %>%
  detailed_entries(
    with = inst,
    what = degree,
    why = detail,
    when = glue::glue("{startYear} --> {endYear}",.na = ""),
    where = where
  )

```

# Skills

```{r SKILLS}

skills %>%
  detailed_entries(
    with = area,
    what = skills
  )

```

# SCHOLARSHIPS/AWARDS

```{r AWARDS}

honors %>%
  detailed_entries(
    with = area,
    what = accomplishment,
    why = detail,
    when = year,
    where = where
  )

```


# Trainings

```{r}
library(tibble)
tribble(
  ~ Title, ~ Date, ~ Institution, ~ Where,
  
"Statistical Analysis and Forest Mapping using Python","26/09/2023-5/10/2023","Forest Research and Training Centre",
"Kathmandu,Nepal", 
  
"Data Analysis With Python Programing Language","14/08/2023-21/08/2023","Forest Research and Training Centre",
"Kathmandu,Nepal",

"Improving forest carbon estimation and degradation monitoring in Nepal","23/07/2022-27/07/2022","USAID,NASA,ICIMOD",
"Chitwan, Nepal" ,
 
"Forest carbon stock measurement using Earth Observation data","10/10/2022-11/11/2022","USAID,NASA,ICIMOD","Kathmandu, Nepal",

"Development of National Land Cover Monitoring System for Nepal","22/08/2022-26/08/2022","USAID,NASA,ICIMOD","Lalitpur, Nepal",
  
#"Dendrochronology and Its Applications","28/06/2022-01/07/2022","Forest Research and Training Centre","Kathmandu,Nepal",  

"Training on Unbaiased Area Estimation and Uncertainty Estimation for Forest Degradation in Nepal","23/05/2022-27/05/22",
"USAID,SilvaCarbon","Pokhara,Nepal",
  
#"Tomograph Handling Training","16/11/2021-28/11/2021","Forest Research and Training Centre","Kathmandu,Nepal",  

#"Data Analysis and Forest Mapping","7/03/2021-16/03/2021","Forest Research and Training Centre","Kathmandu,Nepal",
  
"Training on Mapping Forest Degradation", "25/11/2019-29/11/2019","SilvaCarbon,ICIMOD","Chitawan,Nepal",

"Implementing the Global Land Analysis and Discovery(GLAD) System for forest cover change mapping","24/04/2017-28/04/2017","USAID,SilvaCarbon Global Land Analysis & Discovery","Kathmandu, Nepal",
  
"Introductory Training on LIDAR Data Processing", "18/07/2016–20/07/2016","USAID and US Forest Service-SilvaCarbon","Kathmandu, Nepal",

#"Management Training for Conservation and Development","06/06/2016–11/07/2016","Central Forests Training and Extension Center","Kathmandu, Nepal",

"Advance Training on Statistical Software (R-Package) Handling","08/02/2016–12/02/2016","Forest Research and Training Centre(Formerly Department of Forest Research and Survey)", "Kathmandu, Nepal", 

#"Training Workshop on Dendrochronology","08/11/2015–09/11/2015","Forest Research and Training Centre(Formerly Department of Forest Research and Survey)", "Kathmandu, Nepal",

"Statistical Software (R-Package) Handling Basic Training","01/11/2015–05/11/2015","Forest Research and Training Centre(Formerly Department of Forest Research and Survey)", "Kathmandu, Nepal",
  
#"Scientific Report Writing Training","21/06/2015–23/06/2015","Forest Research and Training Centre(Formerly Department of Forest Research and Survey)", "Kathmandu, Nepal",  
  
"Technical training on Deforestation and Forest Degradation Mapping and Monitoring using Multi-scale Geospatial methods in
the context of REDD+ Initiatives","04/08/2014–08/08/2014","International Centre for Integrated Mountain Development (ICIMOD)","Lalitpur,Nepal",

#"Training for Trainer (ToT) on Forest Fire Management", "05/12/2010–09/12/2010", "Ministry of Forests and Soil conservation and U.S. Department of State and U.S. Forest Service.", "Hetauda, Nepal",

"Statistical Package for Social Science (SPSS)", "28/07/2009–30/07/2009", "Memorial Centre of Excellence (MemCoE)", "Institute of Forestry,Hetauda (Nepal)"
 
) %>%
  detailed_entries(Institution, Date,Title , Where)
```

# Publications

```{r}
bibliography_entries("My_Publication.bib")

```


# Project
- Assessment of Sustainable Forest Management of Community Forest ( A case study of a Sundar Community Forest of Makawanpur District)         submitted in partial fulfillment for the award of the degree of Bachelor of Science in Forestry to Tribhuvan University in 2009.
- 3D landscape metrics along the urban-rural gradient in the Bengaluru, India submitted in George August University in 2019 (Master          Thesis).

# Conference/Workshops

- Participation on ART/TREES Registration Document (TRD) Write-shop held in Thailand, 01-05 August 2023.
- Participation on South-South Exchange on Monitoring and Estimating Emissions from Forest Degradation from 3 to 5 May 2023 at FAO Headquarters, Rome, Italy (Presenter).
- South-South Knowledge Exchange on Measurement, Monitoring, Reporting and Verification systems held in Mozambique,12-17 December 2022(Presenter).
- Participation on Forth GFOI Regional Workshop on Biomass Mapping held in Bogor, Indonesia, 05-09 October 2015.
- Participation on "How is Our Work on Participatory Forest Monitoring informing National Forest Monitoring Systems?" Regional.
  Knowledge Exchange Event on Participatory Forest Monitoring held inLam Dong, Vietnam,18-20 November 2014( Participant).
- Participation on Second GFOI Forest Monitoring Workshop - " SE Asia Technical Initiative" held in Kathmandu, Nepal, 23-28 June, 2014(      Participant)

# Networks and Memberships

- Life Member of Nepal Foresters' Association, Nepal
- Life Member of Makawanpur Forester's Society

# Languages

- Nepali- Mother Tongue 
- English- Proficient user
- Deutsch- Independent user

# References

```{r}
tribble(
  ~ Name,
  ~ Title,
  ~ Contact,
  'Prof. Dr. Christoph Kleinn',
  "Head of Department;Forest Inventory and Remote Sensing, 
  Faculty of Forest Sciences and Forest Ecology,
  Georg-August-University, Goettingen",
  "CKleinn@gwdg.de; +49[0] 39 23473",
  'Deepak Kumar Kharal, Ph.D',
  "Secretary; Ministry of Forests and Environment,Nepal",
  "dkkharal@gmail.com; +977-9841499987",
  'Rajendra KC,Ph.D',
   "Joint-Scretary; Ministry of Forests and Environment,Nepal",
  "rkc.gen@gmail.com ; +977-9851149420"
  
) %>%
  detailed_entries(where = Contact,
                   with = Name,
                   what = Title) 
```



